--- 
title: "Student Coach Minimal book"
author: "by Stephan van der Putten"
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
documentclass: book
bibliography: [book.bib, packages.bib]
biblio-style: apalike
link-citations: yes
description: "Summary of my year starting from Septemebr Leiden University"
---

# Preface {-}

Hello welcome to my book, this will mostly be focused on documenting the the stuff I have learned my last year of the graduates at Leiden University. My name is **Stephan van der Putten** and I will mostly be focusing on summarizing my courses and new developers skills.

```{r include=TRUE}

```

# About this author {-}

This is a _sample_ book written in **Markdown**. You can use anything that Pandoc's Markdown supports, e.g., a math equation $a^2 + b^2 = c^2$.


Remember each Rmd file contains one and only one chapter, and a chapter is defined by the first-level heading `#`.

To compile this example to PDF, you need XeLaTeX. You are recommended to install TinyTeX (which includes XeLaTeX): <https://yihui.org/tinytex/>.

```{r include=FALSE}
# automatically create a bib database for R packages
knitr::write_bib(c(
  .packages(), 'bookdown', 'knitr', 'rmarkdown'
), 'packages.bib')
```
